### 2024-03-12 src/paper.tex
Minor fixes

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\T{num}) &= \{\T{num}\}\\
    \FIRST(\T{var}) &= \{\T{variable}\}\\
    \FIRST(\T{minus}) &= \{\T{minus}\}\\
    \FIRST(\T{to}) &= \{\T{to}\}\\
    \FIRST(\T{print}) &= \{\T{print}\}\\
    \FIRST(\T{return}) &= \{\T{return}\}\\
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\NT{Sub}) &= \FIRST(\T{Primary} \Spc \NT{Sub'})\\
    &= \FIRST(\FIRST(\T{Primary}) \Seq \FIRST(\NT{Sub'}))\\
    &= \FIRST(\{\T{num}, \T{var}\} \Seq \{\T{minus}, \Null\})\\
    &= \FIRST(\{\T{num} \Seq \T{minus}, \T{num}, \T{var} \Seq \T{minus}, \T{variable}\})\\
    &= \{\T{num}, \T{var}\}
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\NT{Stmt}) &= \FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var} \Union \T{print} \Spc \NT{Expr} \Union \NT{return} \Spc \NT{Expr})\\
    \FIRST(\NT{Expr}) &= \FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var}) \cup \FIRST(\T{print} \Spc \NT{Expr}) \cup \FIRST(\NT{return} \Spc \NT{Expr})\\
    &= \{\T{num}, \T{var}\} \cup \{\T{print}\} \cup \{\T{return}\}\\
    &= \{\T{num}, \T{var}, \T{print}, \T{return}\}\\
    \FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var}) &= \FIRST(\FIRST(\NT{Expr}) \Seq \FIRST(\T{to}) \Seq \FIRST(\T{variable}))\\
    &= \FIRST(\{\T{num}, \T{var}\} \Seq \{\T{to}\} \Seq \{\T{variable}\})\\
    &= \FIRST(\{\T{num} \Seq \T{to} \Seq \T{var}, \T{variable} \Seq \T{to} \Seq \T{variable}\})\\
    &= \{\T{num}, \T{var}\}\\
    \FIRST(\T{print} \Spc \NT{Expr}) &= \FIRST(\FIRST(\T{print}) \Seq \FIRST(\NT{Expr}))\\
    &= \FIRST(\{\T{print}\} \Seq \{\T{num}, \T{var}\})\\
    &= \FIRST(\{\T{print}\Seq\T{num}, \T{print} \Seq \T{var}\})\\
    &= \{\T{print}\}\\
    \FIRST(\T{return} \Spc \NT{Expr}) &= \FIRST(\FIRST(\T{return}) \Seq \FIRST(\NT{Expr}))\\
    &= \FIRST(\{\T{return}\} \Seq \{\T{num}, \T{var}\})\\
    &= \FIRST(\{\T{return}\Seq\T{num}, \T{return} \Seq \T{var}\})\\
    &= \{\T{return}\}
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\NT{Stmts}) &= \FIRST(\NT{Stmt} \Spc \NT{Stmts'})\\
    &= \FIRST(\FIRST(\NT{Stmt}) \Seq \FIRST(\NT{Stmts'}))\\
    &= \FIRST(\{\T{num}, \T{var}, \T{print}, \T{return}\} \Seq \{\T{seq},\Null\})\\
    &= \FIRST(\{\T{num} \Seq \T{seq}, \T{var} \Seq \T{seq}, \T{print} \Seq \T{seq}, \T{return} \Seq \T{seq}, \T{num}, \T{variable}, \T{print}, \T{return}\})\\
    &= \{\T{num}, \T{var}, \T{print}, \T{return}\}\\
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FOLLOW(\NT{Start}) &= \{\EOF\}
  \end{aligned}
\end{equation*}

@@

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var}) \Seq \FOLLOW(\NT{Stmt})) &= \FIRST(\{\T{num}, \T{variable}\} \Seq \{\T{seq}, \EOF\})\\
    &= \FIRST(\{\T{num} \Seq \T{seq}, \T{var} \Seq \T{seq}, \T{num} \Seq \EOF, \T{variable} \Seq \EOF \})\\
    &= \{\T{num}, \T{var}\}\\
    \FIRST(\FIRST(\T{print} \Spc \NT{Expr}) \Seq \FOLLOW(\NT{Stmt})) &= \FIRST(\{\T{print}\} \Seq \{\T{seq}, \EOF\})\\
    &= \FIRST(\{\T{print} \Seq \T{seq}, \T{print} \Seq \EOF\})\\
    &= \{\T{print}\}\\
    \FIRST(\FIRST(\NT{return} \Spc \NT{Expr}) \Seq \FOLLOW(\NT{Stmt})) &= \FIRST(\{\T{return}\} \Seq \{\T{seq}, \EOF\})\\
    &= \FIRST(\{\T{return} \Seq \T{seq}, \T{return} \Seq \EOF\})\\
    &= \{\T{return}\}\\
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\T{minus} \Spc \NT{Primary} \Spc \NT{Sub'}) \Seq \FOLLOW(\NT{Sub'})) &= \FIRST(\{\T{minus}\} \Seq \{\T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{minus}, \T{to}, \T{minus} \Seq \T{seq}, \T{minus} \Seq \EOF\})\\
    &= \{\T{minus}\}\\
    \FIRST(\FIRST(\Null) \Seq \FOLLOW(\NT{Sub'})) &= \FIRST(\{\Null\} \Seq \{\T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{to}, \T{seq}, \EOF\})\\
    &= \{\T{to}, \T{seq}, \EOF\}
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\T{num}) \Seq \FOLLOW(\NT{Primary})) &= \FIRST(\{\T{num}\} \Seq \{\T{minus}, \T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{num} \Seq \T{minus}, \T{num} \Seq \T{to}, \T{num} \Seq \T{seq}, \T{num} \Seq \EOF\})\\
    &= \{\T{num}\}\\
    \FIRST(\FIRST(\T{var}) \Seq \FOLLOW(\NT{Primary})) &= \FIRST(\{\T{variable}\} \Seq \{\T{minus}, \T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{var} \Seq \T{minus}, \T{variable} \Seq \T{to}, \T{variable} \Seq \T{seq}, \T{variable} \Seq \EOF\})\\
    &= \{\T{var}\}
  \end{aligned}
\end{equation*}

@@

\begin{algorithm}
  function recognizeStart()
    return recognizeStmts()

@@

  function recognizeStmt()
    return when lookahead
      $\T{num}, \T{var}$ $\rightarrow$ recognizeExpr() $\&\&$ recognizeTerminal($\T{to}$) $\&\&$ recognizeTerminal($\T{to}$)
      $\T{print}$ $\rightarrow$ recognizeTerminal($\T{print}$) $\&\&$ recognizeExpr()
      $\T{return}$ $\rightarrow$ recognizeTerminal($\T{return}$) $\&\&$ recognizeExpr()
      else $\rightarrow$ false

@@

\begin{algorithm}
  function recognizeStart()
    return recognizeStmts()

@@

  function recognizeStmt()
    switch lookahead
      case $\T{num}$:
      case $\T{var}$:
        return recognizeExpr() $\&\&$ recognizeTerminal($\T{to}$) $\&\&$ recognizeTerminal($\T{to}$)
      case $\T{print}$:
        return recognizeTerminal($\T{print}$) $\&\&$ recognizeExpr()
      case $\T{return}$:
        return recognizeTerminal($\T{return}$) $\&\&$ recognizeExpr()
      default:
        return false

>>>>

Za produkcijo $\NT{S} \Arrow \NT{A}$, kjer je $\NT{S}$ začetni simbol, pripravimo funkcijo:
\begin{algorithm}
  function recognizeStart()
    result = recognizeA()
    return when lookahead
      $\EOF$ $\rightarrow$ result
      else $\rightarrow$ false
\end{algorithm}
Preveriti moramo, ali smo prišli do konca vhoda.

@@

\subsubsection*{{\FIRST}}
\begin{equation*}
  \begin{aligned}
    \FIRST(\T{num}) &= \{\T{num}\}\\
    \FIRST(\T{var}) &= \{\T{var}\}\\
    \FIRST(\T{minus}) &= \{\T{minus}\}\\
    \FIRST(\T{to}) &= \{\T{to}\}\\
    \FIRST(\T{print}) &= \{\T{print}\}\\
    \FIRST(\T{return}) &= \{\T{return}\}\\
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\NT{Sub}) &= \FIRST(\T{Primary} \Spc \NT{Sub'})\\
    &= \FIRST(\FIRST(\T{Primary}) \Seq \FIRST(\NT{Sub'}))\\
    &= \FIRST(\{\T{num}, \T{var}\} \Seq \{\T{minus}, \Null\})\\
    &= \FIRST(\{\T{num} \Seq \T{minus}, \T{num}, \T{var} \Seq \T{minus}, \T{var}\})\\
    &= \{\T{num}, \T{var}\}
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\NT{Stmt}) &= \FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var} \Union \T{print} \Spc \NT{Expr} \Union \NT{return} \Spc \NT{Expr})\\
    \FIRST(\NT{Expr}) &= \FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var}) \cup \FIRST(\T{print} \Spc \NT{Expr}) \cup \FIRST(\NT{return} \Spc \NT{Expr})\\
    &= \{\T{num}, \T{var}\} \cup \{\T{print}\} \cup \{\T{return}\}\\
    &= \{\T{num}, \T{var}, \T{print}, \T{return}\}\\
    \FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var}) &= \FIRST(\FIRST(\NT{Expr}) \Seq \FIRST(\T{to}) \Seq \FIRST(\T{var}))\\
    &= \FIRST(\{\T{num}, \T{var}\} \Seq \{\T{to}\} \Seq \{\T{var}\})\\
    &= \FIRST(\{\T{num} \Seq \T{to} \Seq \T{var}, \T{var} \Seq \T{to} \Seq \T{var}\})\\
    &= \{\T{num}, \T{var}\}\\
    \FIRST(\T{print} \Spc \NT{Expr}) &= \FIRST(\FIRST(\T{print}) \Seq \FIRST(\NT{Expr}))\\
    &= \FIRST(\{\T{print}\} \Seq \{\T{num}, \T{var}\})\\
    &= \FIRST(\{\T{print}\Seq\T{num}, \T{print} \Seq \T{var}\})\\
    &= \{\T{print}\}\\
    \FIRST(\T{return} \Spc \NT{Expr}) &= \FIRST(\FIRST(\T{return}) \Seq \FIRST(\NT{Expr}))\\
    &= \FIRST(\{\T{return}\} \Seq \{\T{num}, \T{var}\})\\
    &= \FIRST(\{\T{return}\Seq\T{num}, \T{return} \Seq \T{var}\})\\
    &= \{\T{return}\}
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\NT{Stmts}) &= \FIRST(\NT{Stmt} \Spc \NT{Stmts'})\\
    &= \FIRST(\FIRST(\NT{Stmt}) \Seq \FIRST(\NT{Stmts'}))\\
    &= \FIRST(\{\T{num}, \T{var}, \T{print}, \T{return}\} \Seq \{\T{seq},\Null\})\\
    &= \FIRST(\{\T{num} \Seq \T{seq}, \T{var} \Seq \T{seq}, \T{print} \Seq \T{seq}, \T{return} \Seq \T{seq}, \T{num}, \T{var}, \T{print}, \T{return}\})\\
    &= \{\T{num}, \T{var}, \T{print}, \T{return}\}\\
  \end{aligned}
\end{equation*}

@@

\subsubsection*{{\FOLLOW}}
\begin{equation*}
  \begin{aligned}
    \FOLLOW(\NT{Start}) &= \{\EOF\}
  \end{aligned}
\end{equation*}

@@

\subsubsection*{{\FIRST} $\Seq$ {\FOLLOW}}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\NT{Expr} \Spc \T{to} \Spc \T{var}) \Seq \FOLLOW(\NT{Stmt})) &= \FIRST(\{\T{num}, \T{var}\} \Seq \{\T{seq}, \EOF\})\\
    &= \FIRST(\{\T{num} \Seq \T{seq}, \T{var} \Seq \T{seq}, \T{num} \Seq \EOF, \T{var} \Seq \EOF \})\\
    &= \{\T{num}, \T{var}\}\\
    \FIRST(\FIRST(\T{print} \Spc \NT{Expr}) \Seq \FOLLOW(\NT{Stmt})) &= \FIRST(\{\T{print}\} \Seq \{\T{seq}, \EOF\})\\
    &= \FIRST(\{\T{print} \Seq \T{seq}, \T{print} \Seq \EOF\})\\
    &= \{\T{print}\}\\
    \FIRST(\FIRST(\NT{return} \Spc \NT{Expr}) \Seq \FOLLOW(\NT{Stmt})) &= \FIRST(\{\T{return}\} \Seq \{\T{seq}, \EOF\})\\
    &= \FIRST(\{\T{return} \Seq \T{seq}, \T{return} \Seq \EOF\})\\
    &= \{\T{return}\}\\
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\T{minus} \Spc \NT{Primary} \Spc \NT{Sub'}) \Seq \FOLLOW(\NT{Sub'})) &= \FIRST(\{\T{minus}\} \Seq \{\T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{minus} \Seq \T{to}, \T{minus} \Seq \T{seq}, \T{minus} \Seq \EOF\})\\
    &= \{\T{minus}\}\\
    \FIRST(\FIRST(\Null) \Seq \FOLLOW(\NT{Sub'})) &= \FIRST(\{\Null\} \Seq \{\T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{to}, \T{seq}, \EOF\})\\
    &= \{\T{to}, \T{seq}, \EOF\}
  \end{aligned}
\end{equation*}

@@

\begin{equation*}
  \begin{aligned}
    \FIRST(\FIRST(\T{num}) \Seq \FOLLOW(\NT{Primary})) &= \FIRST(\{\T{num}\} \Seq \{\T{minus}, \T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{num} \Seq \T{minus}, \T{num} \Seq \T{to}, \T{num} \Seq \T{seq}, \T{num} \Seq \EOF\})\\
    &= \{\T{num}\}\\
    \FIRST(\FIRST(\T{var}) \Seq \FOLLOW(\NT{Primary})) &= \FIRST(\{\T{var}\} \Seq \{\T{minus}, \T{to}, \T{seq}, \EOF\})\\
    &= \FIRST(\{\T{var} \Seq \T{minus}, \T{var} \Seq \T{to}, \T{var} \Seq \T{seq}, \T{var} \Seq \EOF\})\\
    &= \{\T{var}\}
  \end{aligned}
\end{equation*}

@@

\begin{algorithm}
  function recognizeStart()
    result = recognizeStmts()
    return when lookahead
      $\EOF$ $\rightarrow$ result
      else $\rightarrow$ false

@@

  function recognizeStmt()
    return when lookahead
      $\T{num}, \T{var}$ $\rightarrow$ recognizeExpr() $\&\&$ recognizeTerminal($\T{to}$) $\&\&$ recognizeTerminal($\T{var}$)
      $\T{print}$ $\rightarrow$ recognizeTerminal($\T{print}$) $\&\&$ recognizeExpr()
      $\T{return}$ $\rightarrow$ recognizeTerminal($\T{return}$) $\&\&$ recognizeExpr()
      else $\rightarrow$ false

@@

\begin{algorithm}
  function recognizeStart()
    result = recognizeStmts()
    if lookahead == $\EOF$
      return result
    else
      return false

@@

  function recognizeStmt()
    switch lookahead
      case $\T{num}$:
      case $\T{var}$:
        return recognizeExpr() $\&\&$ recognizeTerminal($\T{to}$) $\&\&$ recognizeTerminal($\T{var}$)
      case $\T{print}$:
        return recognizeTerminal($\T{print}$) $\&\&$ recognizeExpr()
      case $\T{return}$:
        return recognizeTerminal($\T{return}$) $\&\&$ recognizeExpr()
      default:
        return false
